Hartree-Fock Stability

### 2017-03-08 doc/presentations/GroupMeeting_Fall2016.tex
Modified presentation for Van voorhis lunch

\usetheme{metropolis}
\useoutertheme{metropolis}
\useinnertheme{metropolis}
\usefonttheme{metropolis}
%\usecolortheme{seahorse}   % or your preferred color theme
\usepackage{appendixnumberbeamer}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{xspace}
\usepackage[justification=centering]{caption}
\usepackage{braket}
\usepackage{amsmath}

@@

{%
	\setbeamertemplate{frame footer}{Thouless, D. J. The Quantum Mechanics of Many-Body Systems, 2nd ed.; Dover: 1972. (p. 114)}
\begin{frame}{Hartree-Fock Stability Conditions}
	\begin{itemize}[<+->]
		\item[]{The TDHF solution is given by the Liouville Von-Neumann Equation of Motion,
			\begin{eqnarray}
				i\hbar\frac{\partial \rho}{\partial t} = \left[ T+U, \rho \right],
			\end{eqnarray}
		}
		\item[]{Where U is the self-consistent potential,
			\begin{eqnarray}
				U_{pq} = \sum\limits_{p,q} \left(\rho_{pq,rs} - \braket{pr|sq} \right) \rho_{sr}.
			\end{eqnarray}
		}
		\item[]{Under the restrictions,
			\begin{eqnarray}
				\rho^2 = \rho \quad \textrm{and} \quad \rho^{\dagger} = \rho,
			\end{eqnarray}
		}
		\item[]{and to first order in $\rho_{ai}$, the elements of the density matrix are ,
			\begin{eqnarray}
				\rho_{ai} = C_{ai}, \quad \rho_{ia} = C_{ai}^*.
			\end{eqnarray}
		}
	\end{itemize}
\end{frame}

@@

@@

{%
	\setbeamertemplate{frame footer}{1) Seeger, R.; Pople, J. A. J. Chem. Phys. 1977, 66 (7), 3045.}
\begin{frame}{Hartree-Fock Stability Conditions}
	\begin{itemize}
		\item[]{The eigenvalue equation can be factorized depending on symmetry.} \\~\\
		\item[]{
			\resizebox{0.9\textwidth}{!}{%
			\begin{tabular}{r@{\qquad}cccccc}
				  \multirow{1}{*}{Solution Type} & \multicolumn{6}{c}{Space Type}  \\
				  \cmidrule{2-7}
				  & Real RHF & Complex RHF & Real UHF & Complex UHF & Real GHF & Complex GHF \\
				  \midrule
				  Real RHF    & ${}^1\mathbf{A}' + {}^1\mathbf{B}'$ & ${}^1\mathbf{A}' - {}^1\mathbf{B}'$ & ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & & & \\
				  Complex RHF & - & ${}^1\mathbf{H}'$ & - & \alert{${}^3\mathbf{H}'$} & - & \\
				  Real UHF    & - & - & $\mathbf{A}' + \mathbf{B}'$ & $\mathbf{A}' - \mathbf{B}'$ & $\mathbf{A}'' + \mathbf{B}''$ &  \\
				  Complex UHF & - & - & - &  $\mathbf{H}'$ & - & $\mathbf{H}'$ \\
				  Real GHF    & - & - & - & - & $\mathbf{A} - \mathbf{B}$ &  $\mathbf{A} - \mathbf{B}$  \\
				  Complex GHF & - & - & - & - & - & $\mathbf{H}$ \\
				  \bottomrule
			\end{tabular}}
		\item[] \tiny Table reproduced from Seeger \& Pople$^1$
		}
	\end{itemize}
\end{frame}

@@

\section{Notes on Iterative Subspace Eigenvalue Methods}
{%
\setbeamertemplate{frame footer}{1. Saad, Y. Numerical Methods for Large Eigenvalue Problems; SIAM, 2011.

@@

\end{frame}

@@

@@

@@

\begin{frame}{Matrix Size Scaling}
	\begin{columns}[c] % align columns
		\begin{column}{.4\textwidth}
			\begin{itemize}
				\item {Scales as $2N_{exc}$}
				\item {$N_{occ}$ and $N_{vir}$ both scale with $N_{kpoints}^D$}
			\end{itemize}
		\end{column}
		\hfill
		\begin{column}{0.6\textwidth}
		    \begin{overprint}
			    \onslide<1>\includegraphics[width=\linewidth]{../images/matscale.eps}

@@

\begin{frame}{Algorithm Wall time}
	\begin{columns}[c] % align columns
		\begin{column}{.4\textwidth}
			\begin{itemize}
				\item {Roughly quadratic wrt matrix dimension.}
				\item {Outliers correspond to high condition number}
			\end{itemize}
		\end{column}
		\hfill
		\begin{column}{0.6\textwidth}
		    \includegraphics[width=\linewidth]{../images/overallruntime.eps}
		\end{column}
	\end{columns}
\end{frame}

@@

\section{Concluding Remarks}

{%
\setbeamertemplate{frame footer}{}
\begin{frame}{Next Steps}
	\resizebox{\textwidth}{!}{%
	\begin{tabular}{l c c}
		Objective                 & Human Time   & Computer Time    \\
		\midrule
		Other instabilities in 2D & 30 mins & Week \\
		All 3D & $\frac{1}{2}$ Day&  $>$Weeks? Parallel?
	\end{tabular}}
\end{frame}
}

@@

>>>>

\usetheme{metropolis}
\useoutertheme{metropolis}
\useinnertheme{metropolis}
\usefonttheme{metropolis}
%\usecolortheme{seahorse}   % or your preferred color theme
\usepackage{appendixnumberbeamer}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage[scale=2]{ccicons}
\usepackage{xspace}
\usepackage[justification=centering]{caption}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{verbatim}

@@

\begin{comment}
{%
	\setbeamertemplate{frame footer}{Thouless, D. J. The Quantum Mechanics of Many-Body Systems, 2nd ed.; Dover: 1972. (p. 114)}
\begin{frame}{Hartree-Fock Stability Conditions}
	\begin{itemize}[<+->]
		\item[]{The TDHF solution is given by the Liouville Von-Neumann Equation of Motion,
			\begin{eqnarray}
				i\hbar\frac{\partial \rho}{\partial t} = \left[ T+U, \rho \right],
			\end{eqnarray}
		}
		\item[]{Where U is the self-consistent potential,
			\begin{eqnarray}
				U_{pq} = \sum\limits_{p,q} \left(\rho_{pq,rs} - \braket{pr|sq} \right) \rho_{sr}.
			\end{eqnarray}
		}
		\item[]{Under the restrictions,
			\begin{eqnarray}
				\rho^2 = \rho \quad \textrm{and} \quad \rho^{\dagger} = \rho,
			\end{eqnarray}
		}
		\item[]{and to first order in $\rho_{ai}$, the elements of the density matrix are ,
			\begin{eqnarray}
				\rho_{ai} = C_{ai}, \quad \rho_{ia} = C_{ai}^*.
			\end{eqnarray}
		}
	\end{itemize}
\end{frame}

@@

\end{comment}

@@

{%
	\setbeamertemplate{frame footer}{1) Seeger, R.; Pople, J. A. J. Chem. Phys. 1977, 66 (7), 3045.}
\begin{frame}{Hartree-Fock Stability Conditions}
	\begin{itemize}
		\item[]{The eigenvalue equation can be factorized depending on symmetry.} \\~\\
		\item[]{
			\resizebox{0.9\textwidth}{!}{%
			\begin{tabular}{r@{\qquad}cccccc}
				  \multirow{1}{*}{Solution Type} & \multicolumn{6}{c}{Space Type}  \\
				  \cmidrule{2-7}
				  & Real RHF & Complex RHF & Real UHF & Complex UHF & Real GHF & Complex GHF \\
				  \midrule
				  Real RHF    & ${}^1\mathbf{A}' + {}^1\mathbf{B}'$ & ${}^1\mathbf{A}' - {}^1\mathbf{B}'$ & ${}^3\mathbf{A}' + {}^3\mathbf{B}'$ & - & - & -  \\
				  Complex RHF & - & ${}^1\mathbf{H}'$ & - & \alert{${}^3\mathbf{H}'$} & - & - \\
				  Real UHF    & - & - & $\mathbf{A}' + \mathbf{B}'$ & $\mathbf{A}' - \mathbf{B}'$ & $\mathbf{A}'' + \mathbf{B}''$ & - \\
				  Complex UHF & - & - & - &  $\mathbf{H}'$ & - & $\mathbf{H}'$ \\
				  Real GHF    & - & - & - & - & $\mathbf{A} - \mathbf{B}$ &  $\mathbf{A} - \mathbf{B}$  \\
				  Complex GHF & - & - & - & - & - & $\mathbf{H}$ \\
				  \bottomrule
			\end{tabular}}
		\item[] \tiny Table reproduced from Seeger \& Pople$^1$
		}
	\end{itemize}
\end{frame}

@@

\begin{comment}
\section{Notes on Iterative Subspace Eigenvalue Methods}
{%
\setbeamertemplate{frame footer}{1. Saad, Y. Numerical Methods for Large Eigenvalue Problems; SIAM, 2011.

@@

\end{frame}
\end{comment}

@@

\begin{comment}
{%
\setbeamertemplate{frame footer}{}

@@

			\end{overprint}
		\end{column}
	\end{columns}
\end{frame}
\end{comment}

@@

\begin{frame}{Matrix Size Scaling}
	\begin{columns}[c] % align columns
		\begin{column}{.4\textwidth}
			\begin{itemize}
				\item {Scales as $2N_{exc}$}
				\item {$N_{occ}$ and $N_{vir}$ both scale with $N_{kpoints}^D$}
				\item {Use an iterative subspace method }
				\item {Jacobi-Davidson(-Liu)}
			\end{itemize}
		\end{column}
		\hfill
		\begin{column}{0.6\textwidth}
		    \begin{overprint}
			    \onslide<1>\includegraphics[width=\linewidth]{../images/matscale.eps}

@@

\begin{comment}
\begin{frame}{Algorithm Wall time}
	\begin{columns}[c] % align columns
		\begin{column}{.4\textwidth}
			\begin{itemize}
				\item {Roughly quadratic wrt matrix dimension.}
				\item {Outliers correspond to high condition number}
			\end{itemize}
		\end{column}
		\hfill
		\begin{column}{0.6\textwidth}
		    \includegraphics[width=\linewidth]{../images/overallruntime.eps}
		\end{column}
	\end{columns}
\end{frame}
\end{comment}

@@

{%
\setbeamertemplate{frame footer}{}
\begin{frame}{Dependence on r${}_s$}
	3D data is currently inconclusive. 
	\includegraphics[width=.95\linewidth]{../images/2d3dstability.eps}
\end{frame}

@@

\begin{comment}
\section{Concluding Remarks}
{%
\setbeamertemplate{frame footer}{}
\begin{frame}{Next Steps}
	\resizebox{\textwidth}{!}{%
	\begin{tabular}{l c c}
		Objective                 & Human Time   & Computer Time    \\
		\midrule
		Other instabilities in 2D & 30 mins & Week \\
		All 3D & $\frac{1}{2}$ Day&  $>$Weeks? Parallel?
	\end{tabular}}
\end{frame}
}
\end{comment}
